---
title: "Coding_Challenge4_Markdown_mer0127_kat0084"
author: "Madeline Redd and Katie Temple"
date: "2025-02-27"
output:
  pdf_document:
    toc: true
  md_document:
    variant: gfm  
  word_document: 
    toc: true
  html_document: 
---
# Data Information  
> Noel, Z.A., Roze, L.V., Breunig, M., Trail, F. 2022. Endophytic fungi as promising 
> biocontrol agent to protect wheat from Fusarium graminearum head blight. Plant Disease. 
> [DOI](https://apsjournals.apsnet.org/doi/10.1094/PDIS-06-21-1253-RE)

# Coding Challenge 3 

## Question One 
Explain the following: 
 **YAML header**

A YAML header contains arguments “title”, “author”, “output”, “toc”, 
and “theme” within three dashes (- - -) above and below the arguments. 

 **Literate programming** 

A mix of code and descriptive writing to explain and execute data analysis.  

## Quesiton Two
  - Use geom_pwc() to add t.test pairwise comparisons to the three plots made 
    above. 
  - Save each plot as a new R object, and combine them again with ggarange as 
    you did in question


```{r setup, include=TRUE, echo=TRUE}
library(ggplot2) #version 3.5.1
library(ggpubr) #version 0.6.0
library(ggrepel)  #version 0.9.6
```

Data Set

```{r}
Mycotoxin<- read.csv("MycotoxinData.csv", na.strings = "na")
head(Mycotoxin)

str(Mycotoxin)
```


New Color Palette
```{r}
cbbPalette <- c( "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2",
                 "#D55E00", "#CC79A7","#000000")
```


### DON with pairwise comparisons
```{r, warning=FALSE, fig.width=10, fig.height=7}
plot1 <- ggplot(Mycotoxin, aes(x=Treatment, y=DON, fill=Cultivar)) +
  
  geom_boxplot(outlier.color=NA) +
  geom_point(pch=21, alpha=0.6, color="black", 
             position=position_jitterdodge(dodge.width=0.9)) +
  geom_pwc(aes(group = Treatment),
           method = "t_test", label = "p.signif", hide.ns = TRUE)+
  
  xlab("") +
  ylab("DON (ppm)") +
 
  theme_classic() +
  scale_fill_manual(values= cbbPalette) +
  facet_wrap(~Cultivar)

plot1
```

### X15ADON with pairwise comparisons
```{r, warning= FALSE, fig.width=10, fig.height=7}
plot2 <- ggplot(Mycotoxin, aes(x=Treatment, y=X15ADON, fill=Cultivar)) +
  geom_boxplot(outlier.color=NA) +
  geom_point(pch=21, alpha=0.6, color="black", 
             position=position_jitterdodge(dodge.width=0.9)) +
  geom_pwc(aes(group = Treatment),method = "t_test", label = "p.signif", 
           hide.ns = TRUE)+
  
  xlab("") +
  ylab("15ADON") +
  
  theme_classic() +
  scale_fill_manual(values=cbbPalette) +
  facet_wrap(~Cultivar) 
  

plot2
```

### MassperSeed_mg with pairwise comparisons
```{r, warning= FALSE, fig.width=10, fig.height=7}

plot3 <- ggplot(Mycotoxin, aes(x=Treatment, y=MassperSeed_mg, fill=Cultivar)) +
  geom_boxplot(outlier.color=NA) +
  geom_point(pch=21, alpha=0.6, color="black", 
             position=position_jitterdodge(dodge.width=0.9)) +
  geom_pwc(aes(group = Treatment), method = "t_test", label = "p.signif")+
  
  xlab("") +
  ylab("Seed Mass (mg)") +
  
  theme_classic() +
  scale_fill_manual(values=cbbPalette) +
  facet_wrap(~Cultivar) 
  

plot3
```

### Combining the three plots into one file
```{r, warning=FALSE, fig.height= 15, fig.width= 10}
combined_plots <- ggarrange(plot1, plot2, plot3, 
                           ncol = 1, nrow = 3, 
                           labels = c("A", "B", "C"))

combined_plots

ggsave("combined_plot.jpeg", plot = combined_plots, width =15 , height = 10) 
#Saving Plot to Rproject Folder

```

##Question 6
[Link to github](https://github.com/temkat/CodingChallenge4.git)



